### 2022-06-09 manuscript.tex
Merge pull request #212 from SORTEE-Github-Hackathon/scatterblob-edits [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/995c4b12819cee4b095a8c81c7f5303afab9534e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/995c4b12819cee4b095a8c81c7f5303afab9534e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2470250121

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b1ebce0223ca94ed6e25905a066622e539a2724d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b1ebce0223ca94ed6e25905a066622e539a2724d}{SORTEE-Github-Hackathon/manuscript@b1ebce0}
on June 9, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/995c4b12819cee4b095a8c81c7f5303afab9534e/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/995c4b12819cee4b095a8c81c7f5303afab9534e}{SORTEE-Github-Hackathon/manuscript@995c4b1}
on June 9, 2022.
